Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-30 analysis/paper/paper.Rmd
Add new figure for estimates/95%CI

library(bookdown)
library(knitr)
library(ggplot2)
library(ggpubr)
library(grid)
library(gridExtra)
library(rice.awd.pests)
```

@@

p1 <- ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           group = WMGT,
           shape = WMGT,
           linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Incidence (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = c(x = 0.065, y = 0.76),
        legend.background = element_rect(color = "black", 
                                         size = 0.5,
                                         linetype = "solid"),
        axis.title.x = element_blank())

p2 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_TIL_ShB,
                 group = WMGT,
                 shape = WMGT,
                 linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),)

p3 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_LEAF_ShB,
                 group = WMGT,
                 shape = WMGT,
                 linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Leaf Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none")

@@

p4 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = TShB_incidence,
                 group = NRTE,
                 shape = NRTE,
                 linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Incidence (%)") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = c(x = 0.095, y = 0.69),
        legend.background = element_rect(color = "black", 
                                         size = 0.5,
                                         linetype = "solid"),
        axis.title.x = element_blank()) +
  guides(linetype = guide_legend(ncol = 2),
         shape = guide_legend(ncol = 2))

p5 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_TIL_ShB,
                 group = NRTE,
                 shape = NRTE,
                 linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Severity (%)") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),)

p6 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_LEAF_ShB,
                 group = NRTE,
                 shape = NRTE,
                 linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Leaf Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none")

@@

```{r ShB-W-inc, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
p7 <- ggplot(AUDPS,
             aes(x = WMGT, y = TShB_inc_AUDPS)) +
  geom_boxplot() +
  ylab("Tiller Incidence AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p8 <- ggplot(AUDPS,
       aes(x = WMGT, y = TShB_sev_AUDPS)) +
  geom_boxplot() +
  ylab("Tiller Severity AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p9 <- ggplot(AUDPS,
       aes(x = WMGT, y = LShB_sev_AUDPS)) +
  geom_boxplot() +
  xlab("Treatment") +
  ylab("Leaf Severity AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

@@

```{r ShB-N-sev, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.  Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS. Five different nitrogen treatments were applied to split plots depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
p10 <- ggplot(AUDPS,
              aes(x = NRTE, y = TShB_inc_AUDPS)) +
  geom_boxplot() +
  xlab("Treatment") +
  ylab("Tiller Incidence AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p11 <- ggplot(AUDPS,
              aes(x = NRTE, y = TShB_percent_AUDPS)) +
  geom_boxplot() +
  ylab("Tiller Severity AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p12 <- ggplot(AUDPS,
              aes(x = NRTE, y = LShB_percent_AUDPS)) +
  geom_boxplot() +
  xlab("Treatment") +
  ylab("Leaf Severity AUDPS") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

@@

>>>>

library(bookdown)
library(coda)
library(knitr)
library(ggplot2)
library(ggpubr)
library(grid)
library(gridExtra)
library(rice.awd.pests)
```

@@

p1 <- ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           group = WMGT,
           shape = WMGT,
           linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Incidence (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = c(x = 0.065, y = 0.76),
        legend.background = element_rect(color = "black", 
                                         size = 0.5,
                                         linetype = "solid"),
        axis.title.x = element_blank(),
        strip.background = element_blank())

p2 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_TIL_ShB,
                 group = WMGT,
                 shape = WMGT,
                 linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

p3 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_LEAF_ShB,
                 group = WMGT,
                 shape = WMGT,
                 linetype = WMGT)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Leaf Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "Irrigation",
       shape = "Irrigation") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

p4 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = TShB_incidence,
                 group = NRTE,
                 shape = NRTE,
                 linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Incidence (%)") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = c(x = 0.095, y = 0.69),
        legend.background = element_rect(color = "black", 
                                         size = 0.5,
                                         linetype = "solid"),
        axis.title.x = element_blank(),
        strip.background = element_blank()) +
  guides(linetype = guide_legend(ncol = 2),
         shape = guide_legend(ncol = 2))

p5 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_TIL_ShB,
                 group = NRTE,
                 shape = NRTE,
                 linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Severity (%)") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

p6 <- ggplot(RAW_data,
             aes(x = DAI,
                 y = PERC_LEAF_ShB,
                 group = NRTE,
                 shape = NRTE,
                 linetype = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line") +
  stat_summary(fun.y = "mean",
               geom = "point") +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Leaf Severity (%)") +
  xlab("Days After Inoculation") +
  facet_grid(. ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Rate",
       shape = "N Rate") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank())

@@

```{r ShB-W-inc, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS. Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
p7 <- ggplot(AUDPS,
             aes(x = WMGT, y = TShB_inc_AUDPS)) +
  geom_boxplot() +
  ylab("Tiller Incidence AUDPS") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        strip.background = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p8 <- ggplot(AUDPS,
       aes(x = WMGT, y = TShB_sev_AUDPS)) +
  geom_boxplot() +
  ylab("Tiller Severity AUDPS") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p9 <- ggplot(AUDPS,
       aes(x = WMGT, y = LShB_sev_AUDPS)) +
  geom_boxplot() +
  xlab("Treatment") +
  ylab("Leaf Severity AUDPS") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

@@

```{r ShB-N-sev, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS. Five different nitrogen treatments were applied to split plots depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
p10 <- ggplot(AUDPS,
              aes(x = NRTE, y = TShB_inc_AUDPS)) +
  geom_boxplot() +
  xlab("Treatment") +
  ylab("Tiller Incidence AUDPS") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        strip.background = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p11 <- ggplot(AUDPS,
              aes(x = NRTE, y = TShB_percent_AUDPS)) +
  geom_boxplot() +
  ylab("Tiller Severity AUDPS") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.title.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

p12 <- ggplot(AUDPS,
              aes(x = NRTE, y = LShB_percent_AUDPS)) +
  geom_boxplot() +
  xlab("Treatment") +
  ylab("Leaf Severity AUDPS") +
  theme_classic() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.background = element_blank(),
        strip.text.x = element_blank()) +
  facet_grid(. ~ YEAR,
             scales = "free_x")

@@

##### Estimates plot

```{r estimates-plot, fig.cap="A forest plot of 95% confidence intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE). Five different nitrogen treatments were applied to split plots depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}

models <- readRDS("../data/derived_data/models.Rds")

par(mfcol = c(3, 2))

plot_estimates_paper(models[[1]], main_title = "2015")
mtext("Tiller Incidence", side = 2, line = 6)

plot_estimates_paper(models[[2]])
mtext("Tiller Severity", side = 2, line = 6)

plot_estimates_paper(models[[3]])
mtext("Leaf Severity", side = 2, line = 6)

plot_estimates_paper(models[[4]], main_title = "2016")

plot_estimates_paper(models[[5]])

plot_estimates_paper(models[[6]])
